\documentclass{report}
\author{Tym Pakulski\\Department of Mechanical Engineering, University of Bath\\\\ Supervised by Dr. Roger Ngwompo\\Assessed by Dr. Martin Ansell}
\title{Experimental Assessment of a Krohne Optimass 6400 Mass Flow Meter for Determining CO$_2$ Vapour Quality}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[margin=1in]{geometry}
\usepackage{gensymb}
\usepackage{placeins}
\usepackage{pdflscape}
\usepackage{pdfpages}
\usepackage[toc,page]{appendix}
\usepackage{subcaption}                                            
\usepackage{titlesec}   
\usepackage{titling}
\usepackage{acronym}
\usepackage{hyperref}
\usepackage{float}
\usepackage{wrapfig}
\restylefloat{figure}
\newcommand{\subtitle}[1]{%
  \posttitle{%
    \par\end{center}
    \begin{center}\Large#1\end{center}
    \vskip0.5em}%
}                                           
\titleformat{\chapter}{\normalfont\huge}{\thechapter.}{20pt}{\huge}

\subtitle{Final Year Project Report}
%GUIDELINES: up to 100000 words, intro llit reveiew mehtods results discussion conclusions future work. Margins: 30mm LHS, 10mm RHS, 25 mm top and bottom
\begin{document}
\graphicspath{{figures/}}
%\includepdf[pages={1}]{docs/coverSheet.pdf}
\maketitle
\begin{abstract}
\pagenumbering{roman}
\end{abstract}
\section*{Acronyms}
\begin{acronym}
\acro{CERN}{The European Oranization for Nuclear Research} 
\acro{Nikhef}{National Institute for Subatomic Physics, Amserdam, Netherlands}
\acro{HEP}{High-Energy Physics}
\acro{CMS}{Compact Muon Solenoid - a CERN experiment} 
\acro{LHC}{Large Hadron Collider}
\acro{2PACL}{Two-phase accumulator control loop}
\acro{LS1}{Long Shutdown One} 
\acro{CFCs}{Chlorofluorocarbons} 
\acrodef{Tracker}[SC]{Type of particle detector that tracks the paths of charged particles.} 
\acro{TIF}{Tracker Integration Facility}
\acro{PH-DT}{CERN Physics Department, Detector Technologies Group}
\acro{EGM}{Entrained Gas Management}
\acro{DAQ}{Data Acquisition}
\end{acronym}

\chapter{Introduction}
\pagenumbering{arabic}

\chapter{Literature Review}
\chapter{Methods}
\section{Experiment}
\section{Analysis}
\chapter{Results}
\chapter{Discussion}
\chapter{Conclusions}
\chapter{Future Work}

\begin{thebibliography}{9}
\bibitem{TIF PoS}
P. Tropea \textit{et al.} "Design, construction and commissioning of a 15 kW CO$_2$ evaporative cooling system for particle physics detectors: lessons learnt and perspectives for further development" \textit{Proceedings of Science}, 2014, Paper no. 223

\bibitem{jerome} 
J. Daguin \textit{et al.} "Evaporative $CO_2$ Cooling System for the Upgrade of the CMS Pixel Detector at CERN", \textit{10th IIR Gustav Lorentzen Conference on Natural Refrigerants}, 2012, Paper no. 188.
%Krohne http://optimass6400.krohne.com/#introduction

\bibitem{krohne online}
Krohne Group. "Optimass 6400" Internet: \underline{http://optimass6400.krohne.com/\#\_introduction}, [Feb. 18, 2015]

\bibitem{krohne brochure}
Krohne Group. "Optimass 6400." Brochure. Apr 2013

\bibitem{thome 1}
L. Cheng, G. Ribatski, J. M. Quib$\acute{e}$n, J R. Thome. "New prediction methods for CO$_2$ evaporation inside tubes: Part I - A two-phase flow pattern map and a flow pattern based phenomenological model for two-phase flow frictional pressure drops." \textit{International Journal of Heat and Mass Transfer} vol. 51, pp. 111-124, 2008

\bibitem{bart}
B. Verlaat. "Controlling a 2-phase CO2 loop using a 2-phase accumulator." \textit{International Conference of Refrigeration}, 2007, Beijing, China, ICR07-B2-1565 

\bibitem{bart2}
A.P. Colijn, B. Verlaat. "Evaporative CO$_2$ Heat Transfer Measurements for Cooling Systems of Partical Physics Detectors." \textit{7$^{
th}$ International Conference on Heat Transfer, Fluid Mechanics and Thermodynamics}, 2010, Antalaya, Turkey, HEFAT2010 

\bibitem{mishra}
B. Mishra. "CO$_2$ based two phase cooling test set up for CMS trackers: Comparison of experiments with theoretical models." \textit{CERN CMS Collaboration}

\bibitem{CO2 PoS}
B. Verlaat. "CO2 Cooling Developments for HEP Detectors." \textit{Proceedings of Science}, 2009

\bibitem{emerson youtube}
Emerson Electric Co. Video File: "Demonstration: Coriolis Flowmeter excels with Two-Phase Flow (entrained gas)." Retrieved from \underline{https://www.youtube.com/watch?v=AjtdNxDOeoo}, Jan. 17, 2013, [Mar. 15, 2015]

\bibitem{bath}
M. P. Ansell. "Instructions for ME30227: Engineering project - BEng Academic Year 2014/15." \textit{University of Bath}, 2015

\bibitem{tif web}
P. Tropea. "The CMS PIX Phase I upgrade CO2 cooling: a full scale prototype ready for tests." Internet: \underline{http://ph-news.web.cern.ch/content/cms-pix-phase-i-upgrade-co2-cooling-full-scale-prototype-ready-tests}, Dec. 13, 2013 [Mar. 14, 2015] 

\bibitem{emerson EGM}
D. Wehrs, A. Klosinski. "Entrained Gas Diagnostic with Intelligent Differential Pressure Transmitter." White Paper: \textit{Emerson Process Management}, Jan. 2008, p. 1

\bibitem{processArticle}
K. Parker. "Bent-tube Coriolis flowmeter slated for entrained gas, high-temp applications." \textit{Processing Magazine} (Jul. 1, 2013)

\bibitem{CERN courier}
B. Verlaat, "CO2 cooling is getting hot in high-energy physics." \textit{CERN Courier} (May 31, 2012)

\bibitem{augyrond}
L. Augyrond \textit{et al.} "Void Fraction Measurement in Two-Phse Helium Flow with Electron Energy Attenuation Detector." \textit{Cryogenic Engineering Conference}, Jul. 2001, Madison, WI, USA C-09B-02

\bibitem{zhao}
Y. Zhao, Q. Bi, R. Hu. "Recognition and measurement in theflow pattern and void fraction of gas-liquid two-phase flow in vertical upward pipes using the gamma densitometer." Applied Thermal Engineering 60 (2013) 398e41

\bibitem{x-ray}
D. Bauer, H. Chaves, and C. Arcoumanis. "Measurements of void fraction distribution in cavitating pipe flow
using x-ray CT." Measurement Science and Technology, Issue 23, 2012

\bibitem{bsc}
M. Beker. "Capacitive measurement technique for void fraction measurements in two phase pipe flow." BSc Project, Delft University of Science and Technology, Delft, the Netherlands, Jul. 2005

\bibitem{lecture}
J. M. Doster, "Flow Regime Mapping, Void-Quality Relations and Pressure Drop in Two Phase Flow." Lecture Notes. Nuclear Engineering Department, North Carolina State University 

\bibitem{jean}
B. R. Jean. "A Microwave Sensor for Steam Quality." IEEE Transaction on Instrumentation and Measurement, Aug. 2007

\bibitem{dorfman}
A. Dorfman, E. Fridman. "Vapor quality measurement by a discharging calorimeter." Fluid Phase Equilibria, 244 (2006) 46–51


\end{thebibliography}

\appendix
\end{document}
